Conceptual FD Figure

### 2021-09-17 analysis/figures/conceptual_fig.Rmd
Clean up folders

low_rich <- 
  ggplot(data.frame(x = c(-5, 5)), aes(x)) + 
  stat_function(fun = dnorm, args = list(mean = -3, sd = .9), xlim = c(-5, -1)) +
  stat_function(fun = dnorm, args = list(mean = 3, sd = .9), xlim = c(1, 5)) +
  xlim(c(-5, 5)) +
  #ylim(c(0,1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(.05, 1)) +
  theme_classic() +
  ylab("S") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_text(angle = 0, vjust = 0.5),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  ggtitle("Low")

@@

high_rich <- 
  ggplot(data.frame(x = c(-5, 5)), aes(x)) + 
  #stat_function(fun = dnorm, args = list(mean = -3, sd = .9), xlim = c(-5, -1)) +
  #stat_function(fun = dnorm, args = list(mean = 3, sd = .9), xlim = c(1, 5)) +
  pmap(tibble(mean = c(-3, -2, -1.5, 0, 1.25, 3), 
  sd = rep(0.9, 6)) %>%
    rowwise %>%
    mutate(xlim = list(get_xlim(mean, 2))),
  function(mean, sd, xlim) stat_function(fun = dnorm, args = list(mean = mean, sd = sd), xlim = unlist(xlim))
  )  +
  xlim(c(-5, 5)) +
  #ylim(c(0,1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(.05, 1)) +
  theme_classic() +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  ggtitle("High")
```

Functional Richness
```{r}
low_fric <- 
  ggplot(data.frame(x = c(-5, 5)), aes(x)) + 
  #stat_function(fun = dnorm, args = list(mean = -3, sd = .9), xlim = c(-5, -1)) +
  #stat_function(fun = dnorm, args = list(mean = 3, sd = .9), xlim = c(1, 5)) +
  pmap(tibble(mean = c(-.5, 0,.25), 
  sd = rep(0.9, 3)) %>%
    rowwise %>%
    mutate(xlim = list(get_xlim(mean, 2))),
  function(mean, sd, xlim) stat_function(fun = dnorm, args = list(mean = mean, sd = sd), xlim = unlist(xlim))
  )  +
  xlim(c(-5, 5)) +
  #ylim(c(0,1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(.05, 1)) +
  theme_classic() +
  ylab("FRic") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_text(angle = 0, vjust = 0.5),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

@@

Evenness 
```{r}
low_eve <- 
  ggplot(data.frame(x = c(-5, 5)), aes(x)) + 
  #stat_function(fun = dnorm, args = list(mean = -3, sd = .9), xlim = c(-5, -1)) +
  #stat_function(fun = dnorm, args = list(mean = 3, sd = .9), xlim = c(1, 5)) +
  pmap(tibble(mean = c(-3, -2, -1.5, 0, 1.25, 3), 
  sd = c(1.25, 0.5, 1.25, 1.25, 0.65, 1.25),
  plot_range = c(2.5, 2, 2.5, 2.5, 2, 2.5)) %>%
    rowwise %>%
    mutate(xlim = list(get_xlim(mean, plot_range))) %>%
    select(-plot_range),
  function(mean, sd, xlim) stat_function(fun = dnorm, args = list(mean = mean, sd = sd), xlim = unlist(xlim))
  )  +
  xlim(c(-5.25, 5.25)) +
  #ylim(c(0,1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(.05, 1)) +
  theme_classic() +
  ylab("FEve") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_text(angle = 0, vjust = 0.5),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

@@

Divergence 
```{r}
low_div <-  
ggplot(data.frame(x = c(-5, 5)), aes(x)) + 
  #stat_function(fun = dnorm, args = list(mean = -3, sd = .9), xlim = c(-5, -1)) +
  #stat_function(fun = dnorm, args = list(mean = 3, sd = .9), xlim = c(1, 5)) +
  pmap(tibble(mean = c(-3, -2, -1.5, 0, 1.25, 3), 
  sd = c(0.9, 0.9, 0.55, 0.5, 0.9, 0.9)) %>%
    rowwise %>%
    mutate(xlim = list(get_xlim(mean, 2))),
  function(mean, sd, xlim) stat_function(fun = dnorm, args = list(mean = mean, sd = sd), xlim = unlist(xlim))
  )  +
  xlim(c(-5, 5)) +
  #ylim(c(0,1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(.05, 1)) +
  theme_classic() +
  ylab("FDiv") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_text(angle = 0, vjust = 0.5),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

@@

plot_join <- plot_grid(get_plot_component(low_rich, "ylab-l"), low_rich_fin, high_rich, 
                       get_plot_component(low_fric, "ylab-l"), low_fric_fin, high_fric, 
                       get_plot_component(low_eve, "ylab-l"), low_eve_fin, high_eve, 
                       get_plot_component(low_div, "ylab-l"), low_div_fin, high_div, 
                       nrow = 4, align = 'vh',
                       hjust = -1, axis = "l", scale = 0.9, 
                       label_x = "Trait Axis", label_y = "Abundance")

@@

y.grob <- textGrob("Abundance",  
            gp = gpar(fontsize = 14),
            vjust = 15, rot=90)

x.grob <- textGrob("Trait Axis", hjust = -1.25)

>>>>

low_rich <- 
  ggplot(data.frame(x = c(-5, 5)), aes(x)) + 
  stat_function(fun = dnorm, args = list(mean = -3, sd = .9), xlim = c(-5, -1)) +
  stat_function(fun = dnorm, args = list(mean = 3, sd = .9), xlim = c(1, 5)) +
  xlim(c(-5, 5)) +
  #ylim(c(0,1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(.05, 1)) +
  theme_classic() +
  ylab("S") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_text(angle = 0, vjust = 0.5, face = "bold"),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        plot.title = element_text(hjust = 0.5, face = "bold")) +
  ggtitle("Low")

@@

high_rich <- 
  ggplot(data.frame(x = c(-5, 5)), aes(x)) + 
  #stat_function(fun = dnorm, args = list(mean = -3, sd = .9), xlim = c(-5, -1)) +
  #stat_function(fun = dnorm, args = list(mean = 3, sd = .9), xlim = c(1, 5)) +
  pmap(tibble(mean = c(-3, -2, -1.5, 0, 1.25, 3), 
  sd = rep(0.9, 6)) %>%
    rowwise %>%
    mutate(xlim = list(get_xlim(mean, 2))),
  function(mean, sd, xlim) stat_function(fun = dnorm, args = list(mean = mean, sd = sd), xlim = unlist(xlim))
  )  +
  xlim(c(-5, 5)) +
  #ylim(c(0,1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(.05, 1)) +
  theme_classic() +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        plot.title = element_text(hjust = 0.5, face = "bold")) +
  ggtitle("High")
```

Functional Richness
```{r}
low_fric <- 
  ggplot(data.frame(x = c(-5, 5)), aes(x)) + 
  #stat_function(fun = dnorm, args = list(mean = -3, sd = .9), xlim = c(-5, -1)) +
  #stat_function(fun = dnorm, args = list(mean = 3, sd = .9), xlim = c(1, 5)) +
  pmap(tibble(mean = c(-.5, 0,.25), 
  sd = rep(0.9, 3)) %>%
    rowwise %>%
    mutate(xlim = list(get_xlim(mean, 2))),
  function(mean, sd, xlim) stat_function(fun = dnorm, args = list(mean = mean, sd = sd), xlim = unlist(xlim))
  )  +
  xlim(c(-5, 5)) +
  #ylim(c(0,1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(.05, 1)) +
  theme_classic() +
  ylab("FRic") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_text(angle = 0, vjust = 0.5, face = "bold"),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

@@

Evenness 
```{r}
low_eve <- 
  ggplot(data.frame(x = c(-5, 5)), aes(x)) + 
  #stat_function(fun = dnorm, args = list(mean = -3, sd = .9), xlim = c(-5, -1)) +
  #stat_function(fun = dnorm, args = list(mean = 3, sd = .9), xlim = c(1, 5)) +
  pmap(tibble(mean = c(-3, -2, -1.5, 0, 1.25, 3), 
  sd = c(1.25, 0.5, 1.25, 1.25, 0.65, 1.25),
  plot_range = c(2.5, 2, 2.5, 2.5, 2, 2.5)) %>%
    rowwise %>%
    mutate(xlim = list(get_xlim(mean, plot_range))) %>%
    select(-plot_range),
  function(mean, sd, xlim) stat_function(fun = dnorm, args = list(mean = mean, sd = sd), xlim = unlist(xlim))
  )  +
  xlim(c(-5.25, 5.25)) +
  #ylim(c(0,1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(.05, 1)) +
  theme_classic() +
  ylab("FEve") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_text(angle = 0, vjust = 0.5, face = "bold"),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

@@

Divergence 
```{r}
low_div <-  
ggplot(data.frame(x = c(-5, 5)), aes(x)) + 
  #stat_function(fun = dnorm, args = list(mean = -3, sd = .9), xlim = c(-5, -1)) +
  #stat_function(fun = dnorm, args = list(mean = 3, sd = .9), xlim = c(1, 5)) +
  pmap(tibble(mean = c(-3, -2, -1.5, 0, 1.25, 3), 
  sd = c(0.9, 0.9, 0.55, 0.5, 0.9, 0.9)) %>%
    rowwise %>%
    mutate(xlim = list(get_xlim(mean, 2))),
  function(mean, sd, xlim) stat_function(fun = dnorm, args = list(mean = mean, sd = sd), xlim = unlist(xlim))
  )  +
  xlim(c(-5, 5)) +
  #ylim(c(0,1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(.05, 1)) +
  theme_classic() +
  ylab("FDiv") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_text(angle = 0, vjust = 0.5, face = "bold"),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

@@

plot_join <- plot_grid(get_plot_component(low_rich, "ylab-l"), low_rich_fin, high_rich, 
                       get_plot_component(low_fric, "ylab-l"), low_fric_fin, high_fric, 
                       get_plot_component(low_eve, "ylab-l"), low_eve_fin, high_eve, 
                       get_plot_component(low_div, "ylab-l"), low_div_fin, high_div, 
                       nrow = 4, align = 'vh',
                       hjust = -1, axis = "l", scale = 0.9, 
                       #label_x = "Trait Axis", label_y = "Abundance",
                       rel_widths = c(.5, 1, 1))

@@

y.grob <- textGrob("Abundance",  
            gp = gpar(fontsize = 12),
            vjust = 11, hjust = 0.25, rot=90)

x.grob <- textGrob("Trait Axis", gp = gpar(fontsize = 12), hjust = -0.5)
